### 2021-09-23 README.Rmd
update README
fix duplicate title param

You can install the development version from [GitHub](https://github.com/) with:

@@

@@

>>>>

You can install the development version with:

```r
install.packages("conmat", repos = "https://njtierney.r-universe.dev")
```

Or alternatively you can use `remotes` (although I recommend using the above code)

@@

We can extract out the ABS age population data using `abs_age_lga` like so:

@@

Note that you need to use the exact LGA name - you can look up LGA names in the data set `abs_lga_lookup`:

```{r abs-lga-lookup}
abs_lga_lookup
```

We can then extrapolate this data from polymod and plot a matrix, below:
